\section{Equivalences}\label{sec:equivalences}

In this section we prove that the categories $\DD_3$ and $\DD_4$ are indeed
presentations for quantum subgroups of $\GG_2(q_3)$ and $\GG_2(q_4)$, respectively.
More details of the argument used may be found in \cite{cain_noah}.
It is necessary to note that from \cite{gannon_exotic_q_subgroups_extensions-II} we know that the only nontrivial Etale algebras 
in $\ol{\Rep(U_{q_3}(\gg_2))}$ and $\ol{\Rep(U_{q_4}(\gg_2))}$ are $A_3$ and $A_4$, respectively.

We first state and prove the theorem at level 4.

\begin{theorem}\label{thm:level-4}
    There is a monoidal equivalence
    \[
        \Ab(\ol{\DD_4}) \cong \ol{ \Rep(U_{q_4}(\gg_2))}_{A_4}.
    \]
\end{theorem}

We first note that $\Ab(\ol{\DD_4})$ is the category of modules for {\it some} Etale algebra.

\begin{proposition}
    There is an Etale algebra $B_4$ such that 
    \[
        \Ab(\ol{\DD_4}) \cong \ol{ \Rep(U_{q_4}(\gg_2))}_{B_4}.
    \]
\end{proposition}

\begin{proof}
    Recall the $\dagger$-embedding $\ol{\GG_2(q_4)} \hookrightarrow \ol{\DD_4}$ of Corollary~\ref{cor:D4-dagger-emb}.
    From here we take Karoubi completion, which induces a functor 
    \[
        \Ab( \ol{\GG_2(q_4)} ) \hookrightarrow \Ab( \ol{\DD_4} )
    \]
    which is faithful exact.
    By Lemma~\ref{lem:exact-functor}, we deduce that
    \[
        \Ab(\ol{\DD_4}) \cong \Ab( \ol{\GG_2(q_4)} )_{B_4}
    \]
    for some Etale algebra object $B_4$.
    But it is well known \cite{Kuperberg} that 
    \[
        \Ab( \ol{\GG_2(q_4)} ) \cong \ol{ \Rep(U_{q_4}(\gg_2))}.
    \]
\end{proof}

Now we are in a position to prove Theorem~\ref{thm:level-4}.

\begin{proof}[Proof of Theorem~\ref{thm:level-4}]
    As we noted before, the only candidates for $B_4$ are $A_4$ and $\unit$.
    Thus it will suffice to demonstrate that 
    \[
        \Ab(\ol{\DD_4}) \not\cong \ol{ \Rep(U_{q_4}(\gg_2))} \cong \ol{ \Rep(U_{q_4}(\gg_2))}_{\unit}.
    \]
    
    The induced functor $\Ab( \ol{\GG_2(q_4)} ) \hookrightarrow \Ab( \ol{\DD_4} )$, whose existence we noted above,
    is defined to be such that the following diagram commutes:
    \[
    \xymatrix@C=60pt@R=45pt{
    \ol{\GG_2(q_4)} \ar@{^{(}->}[r]^{} \ar@{^{(}->}[d]^{} & \ol{\DD_4} \ar@{^{(}->}[d]^{\JJ} \\
    \ol{ \Rep(U_{q_4}(\gg_2))} \ar@{^{(}->}[r]^{} & \Ab( \ol{\DD_4} )
     }
    \]
    By Lemma~\ref{lem:exact-functor} there is an equivalence $\KK$ such that, up to isomorphism, the diagram
    \[
    \xymatrix@C=60pt@R=45pt{
    \ol{\GG_2(q_4)} \ar@{^{(}->}[r]^{} \ar@{^{(}->}[d]^{} & \ol{\DD_4} \ar@{^{(}->}[d]^{\JJ} \\
    \ol{ \Rep(U_{q_4}(\gg_2))} \ar@{^{(}->}[r]^{} \ar[dr]^{\FF_{B_4}} & \Ab( \ol{\DD_4} ) \ar[d]^{\KK} \\
      & \ol{ \Rep(U_{q_4}(\gg_2))}_{B_4} \\
     }
    \]
    commutes.

    Now, chasing the object $1_{ \ol{\GG_2(q_4)}}$ through the leftmost path on this diagram, we have 
    \[
        1_{ \ol{\GG_2(q_4)}} \mapsto V_{\Lambda_1} \mapsto B_4 \otimes V_{\Lambda_1}.
    \]
    If it was true that $B_4\cong \unit$, we would have 
    \[
        \dim \Hom_{\ol{ \Rep(U_{q_4}(\gg_2))}_{B_4}}((B_4 \otimes V_{\Lambda_1})^{\otimes 2} \to B_4 \otimes V_{\Lambda_1}) = 1.
    \]
    Now let us chase the object $1$ along the top rightmost path to demonstrate that this is not the case.
    Along this second path we have
    \[
        1_{ \ol{\GG_2(q_4)}} \mapsto 1_{\ol{\DD_4}} \mapsto \JJ(1_{\ol{\DD_4}}) \mapsto \KK\circ\JJ(1_{\ol{\DD_4}}).
    \]
    Set $\CC_4 \coloneq \ol{ \Rep(U_{q_4}(\gg_2))}$.
    Now we note that
    \begin{align*}
        \dim \Hom_{(\CC_4)_{B_4}}((B_4 \otimes V_{\Lambda_1})^{\otimes 2} \to B_4 \otimes V_{\Lambda_1}) & = 
            \dim \Hom_{(\CC_4)_{B_4}}((\KK\circ\JJ(1_{\ol{\DD_4}}))^{\otimes 2} \to \KK\circ\JJ(1_{\ol{\DD_4}})) \\
        & = \dim \Hom_{\Ab( \ol{\DD_4} )}((\JJ(1_{\ol{\DD_4}}))^{\otimes 2} \to \JJ(1_{\ol{\DD_4}})) \\
        & = \dim \Hom_{\ol{\DD_4} }( (1_{\ol{\DD_4}})^{\otimes 2} \to 1_{\ol{\DD_4}}) \\
        & = \dim \Hom_{\ol{\DD_4} }( 2_{\ol{\DD_4}} \to 1_{\ol{\DD_4}}) \\
        & = 2.
    \end{align*}
    Since $B_4 \not\cong\unit$, we must have $B_4 \cong A_4$; the theorem is proved.
\end{proof}


The category $\DD_3$, whose $\Z_3$-like structure constants are given in the Mathematica notebook
\verb|/code/level-3/nb-6_verify-g.nb|, admits an analogous theorem at level 3.

\begin{theorem}\label{thm:level-3}
    There is a monoidal equivalence
    \[
        \Ab(\ol{\DD_3}) \cong \ol{ \Rep(U_{q_3}(\gg_2))}_{A_3}.
    \]
\end{theorem}

The proof of Theorem~\ref{thm:level-3} is analogous to the argument given above.